\documentclass[a4paper, english, 10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{lmodern}
\usepackage{tgpagella}

\usepackage{geometry}
\geometry{ hmargin=3cm, vmargin=3.5cm }

\usepackage{fancyhdr}
\pagestyle{fancy}

\makeatletter
\newcommand{\@templatetitle}{On Strategyproof Picking Sequences} % Le titre
\newcommand{\@templatesubtitle}{~}
\newcommand{\@templateauthor}{Sylvain B.} % Les auteurs
\newcommand{\@templatedate}{\today} % Les auteurs
\newcommand{\@templatekeywords}{} % Les mots-clefs
\newcommand{\@templatesubject}{} % Le sujet
\makeatother

\makeatletter
\fancyhf{} % clear all fields
\fancyhead[C]{\nouppercase{\fontfamily{\sfdefault}\fontseries{m}\fontshape{sf}\footnotesize\selectfont\color{gray} \@templatetitle}} % Insérer le titre ici
\renewcommand{\headrule}{\color{lightgray}\hrule}
\fancyfoot[C]{\fontfamily{\sfdefault}\fontseries{m}\fontshape{sf}\small\selectfont\thepage}
\makeatother

\usepackage{natbib}
\renewcommand{\cite}[1]{\citep{#1}}
\usepackage{babel}

\setlength{\overfullrule}{10pt}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{latexsym}                   % Symboles
\usepackage{mathrsfs}                   % Oh, les jolies lettres calligraphiées !
\usepackage{stmaryrd}                   % Pour avoir les délimiteurs entiers
\usepackage[amsmath, thmmarks]{ntheorem} % Un environnement theorem custom
\usepackage{breakcites}
\usepackage{stmaryrd}
\usepackage{booktabs}
\usepackage{listings} % Pour insérer du code source


\usepackage{tcolorbox,listings}
\usepackage{fullpage}
\usepackage{color}

\definecolor{darkWhite}{rgb}{0.94,0.94,0.94}

\lstset{
	backgroundcolor=\color{darkWhite},
	breakatwhitespace=false,
	breaklines=true,
	captionpos=b,
	commentstyle=\color{red},
	deletekeywords={...},
	escapeinside={\%*}{*)},
	extendedchars=true,
	keepspaces=true,
	keywordstyle=\color{blue},
	language=C,
	morekeywords={*,...},
	showspaces=false,
	showstringspaces=false,
	showtabs=false,
	stepnumber=1,
	stringstyle=\color{gray},
	tabsize=4,
	title=\lstname,
}

\lstdefinestyle{frameStyle}{
	basicstyle=\footnotesize,
	numbers=left,
	numbersep=20pt,
	numberstyle=\tiny\color{black}
}

\tcbuselibrary{listings,skins,breakable}

\newtcblisting{customFrame}{
	arc=0mm,
	top=0mm,
	bottom=0mm,
	left=3mm,
	right=0mm,
	width=\textwidth,
	listing only,
	listing options={style=frameStyle},
	breakable
}


\usepackage{tikz}

\usepackage[pdftex]{hyperref}

\usepackage{theorem}
\theoremsymbol{$\blacksquare$}
{\theorembodyfont{\rmfamily}\newtheorem{exemple}{Exemple}}

\newcommand{\fixme}[1]{{\small\color{red}[FIXME : #1]}}
\makeatletter
\newcommand{\Omit}[1]{\ifhmode \@bsphack \@esphack \fi}
\makeatother

\definecolor{mycyan}{rgb}{0,0.2,0.4}
\hypersetup{%
  colorlinks=true,
  citecolor=mycyan,
  linkcolor=mycyan,
  anchorcolor=mycyan,
  urlcolor=mycyan,
  pdfstartview=FitH,
  pdfdisplaydoctitle=true,
  %pdfwindowui=false,
  pdftoolbar=true,
  pdfmenubar=true
}

\makeatletter
\hypersetup{%
  pdftitle={\@templatetitle},
  pdfauthor={\@templateauthor},
  pdfsubject={\@templatesubject},
  pdfkeywords={\@templatekeywords}
}
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Notations

\newcommand{\ee}{\mathcal{E}}
\newcommand{\var}[1]{\mathbf{#1}}
\newenvironment{resume}{
  \textbf{Abstract}\quad\itshape
}{
  \vskip\parskip
}
\newcommand{\motsclefs}[1]{\textbf{Keywords} \quad #1\\\vskip\parskip}

\DeclareMathOperator{\argmax}{argmax}
\newtheorem{definition}{Definition}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%





\makeatletter
\title{\@templatetitle}
\author{\@templateauthor}
\date{\@templatedate}
\makeatother

\makeatletter
\renewcommand{\maketitle}{
  \begin{center}
    {\LARGE\sffamily\bfseries \@templatetitle}\\\hrulefill\\
    {\large \@templatesubtitle}\\\vskip0.5cm
    \@templateauthor\\
    \@templatedate\\\vskip0.5cm
  \end{center}
}
\makeatother

\begin{document}
\renewcommand{\labelitemi}{\tikz\fill[rounded corners=1pt] (0, 0) -- (4pt, 2.5pt) -- (0pt, 5pt) -- cycle;}

\thispagestyle{plain}

\maketitle

\begin{abstract}
  This short note is about strategyproof picking sequences, namely,
  picking sequences where the agents pick all their objects in a row,
  in a serial dictatorship fashion. Hopefully, the computation of the
  fairest sequence is much easier in this case.
\end{abstract}


\section{Two agents}

We assume that there are two agents Alice and Bob ($A$ and $B$) and
$m$ objects labeled from 1 to $m$. We consider that the agents have
Borda utility functions. We assume Full Independence assumption: the
benevolent dictator is ignorant of Alice's and Bob's actual
preferences, but assumes that all the ordinal are equally probable.

We focus on picking policies of the following form:
\[
  \pi^k = \underbrace{AA \dots A}_{k \text{ times}}\underbrace{BB \dots B}_{m - k \text{ times}}
\]

The question is the following one. What is the integer $k$ such that
$\pi^k$ maximizes the egalitarian expected utility? In other words, we
look for:
\[
  \argmax_{k \in \{ 1, ... m \}}(\min(\overline{u(A, \pi^k)}, \overline{u(B, \pi^k)}))
\]

Of course, we assume that both Alice and Bob are rational players:
they act according to their dominant strategy. Here, the only dominant
strategy for both of them is to pick their preferred items (truthful
strategy).

\subsection{Computation of expected utility}

\subsubsection{Alice}

Alice's expected utility can be computed immediately. No matter what
Bob's preferences are she will always pick her $k$ best objects. Hence:
\[
  \overline{u(A, \pi^k)} = \frac{m(m+1)}{2} - \frac{(m-k)(m-k+1)}{2}
\]

We will assume without loss of generality, that Bob has the following
preferences over items: $1 \succ 2 \succ ... \succ m$. Concerning
Alice, all the linear orders on $\{ 1, ..., m \}$ are equally probable
(Full Independence assumption).

\subsubsection{Bob}
\label{BobTh}

Bob's expected utility is less immediate to compute. Let us introduce the following
notation:

\begin{definition}
  Let $n$, $k \leq n$ and $t \leq \frac{n(n+1)}{2}$ be three
  integers. Then:
  \[
    S(n, k, t) = \left|\{\mathcal{S} \subset \{1, \dots, n\}\ |\ \sum_{x_i \in \mathcal{S}} x_i = t \text{ and } |\mathcal{S}| = k\}\right|.
  \]
  In other words, $S(n, k, t)$ is the number of different subsets of
  $k$ elements from $\{1, \dots, n\}$ that sum up to $t$.
\end{definition}


The possible utilities for Bob range from $\frac{(n-k)(n-k+1)}{2}$ (if
the $k$ items picked by Alice are Bob's $k$ top ones) to
$\frac{n(n+1)}{2} - \frac{k(k+1)}{2}$ (if the $k$ items picked by
Alice are Bob's $k$ bottom ones). More generally, Bob will get utility
$U$ if and only the items picked by Alice are worth
$\frac{n(n+1)}{2} - U$ for Bob. There are 
$S(n, k, \frac{n(n+1)}{2} - U)$ subsets of that kind. 
For the Alice's utilitie the order of the k firsts ones and the n-k lasts ones  doesn't matter (the k firsts will all be picked and the n-k last not) so permutation won't change the utility of Bob (U).
So Alice could choose $S(n, k, \frac{n(n+1)}{2} - U) \times k! \times (n-k)!$ linear orders verifying this property among the $n!$ possible ones.


\subsubsection{Compute(S(n,k,t))}
\begin{customFrame}
def subset_sum(n, k, target, memo=None):
	""" Computes (and returns) the number of possibilities of taking k different integers between 1 and n who sum up to target. """
	
	if memo is None:
		return subset_sum(n, k, target, [[[-1 for _ in range(target + 1)]
										for _ in range(k + 1)] for _ in range(n + 1)])
	if k == 0:
		return int(target == 0)
	elif target <= 0 or n == 0:
		return 0
	if memo[n][k][target] == -1:
		memo[n][k][target] = (
			subset_sum(n - 1, k - 1, target - n, memo) + 
			subset_sum(n - 1, k, target, memo))
	return memo[n][k][target]

\end{customFrame}

\begin{description}
	\item[Termination:] The natural n is decremented at each call of subset-sum, because $\mathbb{N}$ is well-ordered the algorithm end.
	\item[Correctness:] By induction over (n,k,t) (with lexicographic order):
	
	
		\begin{description}
			\item[Init :]
			\begin{description}
			\item[If memo is None:] Is called once, to pre-initialize the table used for memoization
			\item[If $k==0$ :] A subset of zero element is unique and can only sum up to 0, so $S(n,0,0) = 1$ and $S(n,0,t) = 0$ for $t > 0$ 
			\item[If $target <= 0$ :] Every utilitie is a strictly positive integer so it is impossible to reach a negative target
			\item[If $n==0$ :] There is no subset of the empty set
			\end{description}
			\item[Inductive step :] Let suppose that subset\_sum(n',k',target',memo) is egal to S(n',k',target') for every (n',k',target') < (n,k,target) then:
			 If $ memo(n,k,target) == -1 $ (i.e if subset\_sum(n,k,target,memo) hasn't be called before) then there is two distincts cases:
			  \begin{itemize}
			  	\item Alice pick the object of utility n, so she had to pick another k-1 objects from $\{1, \dots, n-1\}$ such as it sum up to t' = target - n, which is exactly S(n-1,k-1,target - n, memo) so subset\_sum(n-1,k-1,target - n, memo) by hypothese of induction
			  	\item Alice don't pick the object of utility n, so she has still k objects summing to target to choose from $\{1, \dots, n-1\}$, which is subset\_sum(n-1,k,target , memo) by hypothese of induction
			  \end{itemize}
		  Finally subset\_sum(n,k,t) = S(n - 1, k - 1, target - n, memo) + S(n - 1, k, target, memo)) = S(n,k,t)
		  We store that value in memo not to compute it every time we need it, and we return it
		  

			
			
			 
		\end{description}
\end{description} 

\subsubsection{Computing bob expexted utility}

	\begin{customFrame}
	def bobs_expected_utility(n, k, memo=None):
	"""
	Computes (and returns) the expected utility for Bob, assuming
	that there are n objects, and Alice picks the first k ones.
	"""
	
	total_utility = int(n * (n + 1) / 2)
	min_picked = int(k * (k + 1) / 2)
	max_picked = total_utility - int((n - k) * (n - k + 1) / 2)
	return sum((total_utility - picked) * subset_sum(n, k, picked, memo)
	for picked in range(min_picked, max_picked + 1)) * factorial(k) * factorial(n - k) / factorial(n)		
	\end{customFrame}
This algorithm is the direct application of \ref{BobTh}

\subsection{Optimal policy}

\subsubsection{Compute optimal policy}

	\begin{customFrame}
	def optimal_cut(n):
	"""
	Computes (and returns) the optimal cut for n object. In other words,
	this number is the integer k that guarantees the best egalitarian expected
	utility for Alice and Bob if Alice picks the first k items and Bob the n-k
	remaining ones.
	"""
	total_utility = int(n * (n + 1) / 2)
	last_min = 0
	memo = -np.ones((n + 1, total_utility + 1, total_utility + 1), dtype=np.float)
	for k in range(1, n + 1):
	alice = total_utility - int((n - k) * (n - k + 1) / 2)
	bob = bobs_expected_utility(n, k, memo)
	if alice > bob:
	return (k - 1 if last_min > min(alice, bob) else k,
	alice, bob)
	last_min = min(alice, bob)
	assert False, "We shouldn't be here..."
	return	
\end{customFrame}

\subsubsection{Some numbers}

\begin{tabular}{lll}
  \toprule
  $m$ & $\hat{k}$ & $\hat{k} / m$\\
  \midrule
  10 & 4 & 0.4\\
  20 & 8 & 0.4\\
  30 & 12 & 0.4\\
  40 & 15 & 0.375\\
  50 & 19 & 0.38\\
  60 & 23 & 0.38333...\\
  100 & 38 & 0.38\\
  \bottomrule
\end{tabular}



% \bibliographystyle{plainnat-fr}
% \bibliography{partage}


\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
